---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Jocelyn Matusiak
  - Jordan Alfano
  - Julia Candee
  - Sophia Frisiras

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

---

```{r}
library(tidyverse)
library(hrbrthemes)
library(skimr)
```




  
About this project :clap:
##
  
```{r}
day_wise <- read_csv('https://jem10126.github.io/day_wise.csv')
nvars <- format(round(ncol(day_wise), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(day_wise), 0), 
                nsmall=0, 
                big.mark=",")
```

- Here is the paged table using `rmarkdown::paged_table()` with the `results = 'asis'` chunk option.

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(day_wise) 
```
<br>

The number of variables is `r nvars`; the number of observations is `r nobs`.

<br>



## Introduction
  - Why does this project matter?
  
  - This project matters because it assess the rate at which people are 
  contracting and healing from the COVID-19 virus at a daily rate.
  
  - Our data visualization entails both Deaths and Recovered 
  are increasing at an exponential rate. This provides the assumption 
  that while many may be dying there are a greater amount recovering. 
  In the real world this provides hope for those who are suffering from 
  the virus. Our data transformation further proves the point that there are 
  more total recovered per day than the mean amount of deaths.

## Data Summary

- Summary statistics (Use `skimr::skim(day_wise)`)


```{r}
skimr::skim(day_wise)
```
## Data Visualization

```{r}
day_wise %>% 
  ggplot(aes(x = log(Deaths), 
             y = log(Recovered))) +
  geom_point(alpha = .1,color = 'purple') +
  geom_smooth(method = lm, se = F) +
  theme_bw() +
  theme(legend.position = 'top')
```

## Data Transformation


```{r}
day_wise1 <- day_wise %>% 
  group_by(Deaths, Recovered) %>% 
  summarise(Recovered_tot = sum(Recovered, na.rm = T),
            Deaths_mean = round(mean(Deaths, na.rm = T), 2),
            .groups = "drop") 
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(day_wise1) 
```


<br><br><br><br>

# References

- [https://quarto.org/docs/output-formats/html-basics.html](https://quarto.org/docs/output-formats/html-basics.html)

- [https://quarto.org/docs/websites/](https://quarto.org/docs/websites/)

- [R for Data Science](http://r4ds.hadley.nz) by [Hadley Wickham](https://hadley.nz)

## Group relevancy

We wanted to include how much Sophia has helped in our project 
while not being able to do it herself. She has attended all meetings 
with us as a group and helped us whenever we needed extra assistance.












