---
title: DANL Project
subtitle: "Data-Driven Mastery: COVID19"
author: 
  - Jocelyn Matusiak
  - Jordan Alfano
  - Julia Candee
  - Sophia Frisiras

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

---

```{r}
library(tidyverse)
library(hrbrthemes)
library(skimr)
```

## Introduction
  - Why does this project matter?
  
  - This project matters because it assess the rate at which people are 
  contracting and healing from the COVID-19 virus at a daily rate.
  
  - Our data visualization entails both Deaths and Recovered 
  are increasing at an exponential rate. This provides the assumption 
  that while many may be dying there are a greater amount recovering. 
  In the real world this provides hope for those who are suffering from 
  the virus. Our data transformation further proves the point that there are 
  more total recovered per day than the mean amount of deaths.

  
## About this project:
  - We initiated the process by generating a fresh dataset in R-studio, 
  utilizing the path name of the "Day-Wise Covid-19" dataset. Below, you will
  find the resulting table produced through our code. The table is specifically
  designed to highlight the daily number of COVID-19 cases, as well as the 
  status of those who were diagnosed - whether they have recovered, 
  passed away, or are still actively ill.(Sophia)


## Data
  
```{r}
day_wise <- read_csv('https://jem10126.github.io/day_wise.csv')
nvars <- format(round(ncol(day_wise), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(day_wise), 0), 
                nsmall=0, 
                big.mark=",")
```

- Here is the paged table using `rmarkdown::paged_table()` with the `results = 'asis'` chunk option.

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(day_wise) 
```
<br>

The number of variables is `r nvars`; the number of observations is `r nobs`.

<br>




## Data Summary

- Summary statistics (Use `skimr::skim(day_wise)`)

  - We are now performing summary statistics on our data set. We use the skim () 
code to find the mean, median, minimum,  maximum, and quantile values. 
This gives us an overview of our dataset and helps us determine relationships
between our variables.(Sophia)


```{r}
skimr::skim(day_wise)
```

## Data Visualization

  - Our plot represents the relationship between the logarithmic of deaths and 
  the logarithmic of recoveries for the daily number of covid cases. For 
  this section we decided to create a scatterplot using the geom_point () code.
  Along with that we used geom_smooth () to create a second line to help 
  determine the overall pattern of our data. To better the aesthetics of 
  our graph using the theme () code.(Sophia)

```{r}
day_wise %>% 
  ggplot(aes(x = log(Deaths), 
             y = log(Recovered))) +
  geom_point(alpha = .1,color = 'purple') +
  geom_smooth(method = lm, se = F) +
  theme_bw() +
  theme(legend.position = 'top')
```

## Data Transformation

  - For the Data Transformation section, we created another new data frame 
  called “day_wise1”. In this data frame, we used the group_by () function to 
  group COVID-19 cases by the total amount of recovered cases and the mean 
  amount of deaths. This new data frame helps to better illustrate that 
  even though there may be a significant number of deaths from COVID-19, 
  there are more recoveries. (Sophia)

```{r}
day_wise1 <- day_wise %>% 
  group_by(Deaths, Recovered) %>% 
  summarise(Recovered_tot = sum(Recovered, na.rm = T),
            Deaths_mean = round(mean(Deaths, na.rm = T), 2),
            .groups = "drop") 
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(day_wise1) 
```


<br><br><br><br>

# References

- [https://quarto.org/docs/output-formats/html-basics.html](https://quarto.org/docs/output-formats/html-basics.html)

- [https://quarto.org/docs/websites/](https://quarto.org/docs/websites/)

- [R for Data Science](http://r4ds.hadley.nz) by [Hadley Wickham](https://hadley.nz)

## Group relevancy

We wanted to include how much Sophia has helped in our project 
while not being able to do it herself. She has attended all meetings 
with us as a group and helped us whenever we needed extra assistance.












